On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-04-11 manuscript/manuscript.tex
added pp-plots to manuscript

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_fitted}
  \caption{PP-plot for the p-values obtained from KS tests with unspecified
    parameters with sample size $n = 200$ based on 1000 replicats. The data
    generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
  }
  \label{fig:pp_f}
\end{figure}

@@

The invalidity of the standard statistic for serially dependent data can be
illustrated by a simple simulation study. Consider a first-order autoregressive
or AR(1) model with marginal standard normal distribution. For each AR
coefficient $\psi \in \{-0.3, 0.2, 0.1, 0, 0.1, 0.2, 0.3\}$, we generated 1000
series of length 100. For each series, we applied the KS statistic
in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(0, 1)$
marginally. The histograms of the p-values from $1000$ replicates for all the
$\psi$ values are displayed in Figure~\ref{fig:hist_correlation}. When
$\phi \ne 0$, the histograms do not look likely to be generated from a standard
uniform distribution. Positive $\psi$ values led to p-values with a distribution
function higher than the standard uniform distribution function and, hence,
conservative tests. Negative $\psi$ values led to p-values with a distribution
function lower than the standard uniform distribution and, hence, liberal
tests. The larger the magnitude of
$\psi$, the bigger the deviation from the desired level.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{PP-plots for the p-values obtained from KS test with serial
    dependence discarded and sample size $n = 200$ based on 1000
    replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
  }
  \label{fig:pp_s}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{PP-plots for the p-values obtained from KS test with serial
    dependence accounted for through a working ARMA model and $n = 200$ based on
    1000 replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
  }
  \label{fig:pp_ss}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{PP-plots for the p-values obtained from KS test with unspecified
    parameters and serial
    dependence accounted for through a working ARMA model and $n = 200$ based on
    1000 replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
  }
  \label{fig:pp_ss}
\end{figure}

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an AR(1)
dependence structure by taking the lag-1 sample auto-spearman rho. However, we
can show that as long as the AR(1) assumption is a close approximation, the
correction still provides a reasonable approximation that can be useful for
practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the
procedure performed on data generated with dependence structures of  MA(1),
ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for
dependence clearly deviates from a uniform distribution of p-values. Parametric
bootstrap provides some correction but does not account for dependence, so
therefore the results of the copula remedy are more accurate and favorable.
In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
to our assumption of AR(1) that the results are reasonable. AR(2) however
appears to be just far enough from our assumption, showing a limitation of the
procedure.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.5\textwidth]{pp_f.pdf}
  \caption{PP-plot for the p-values obtained from KS tests with unspecified
    parameters with sample size $n = 200$ based on 1000 replicats. The data
    generating models were $N(8, 8)$ and $\Gamma(8, 1)$.
  }
  \label{fig:pp_f}
\end{figure}

@@

The invalidity of the standard statistic for serially dependent data can be
illustrated by a simple simulation study. Consider a first-order autoregressive
or AR(1) model with marginal standard normal distribution. For each AR
coefficient $\psi \in \{-0.3, 0.2, 0.1, 0, 0.1, 0.2, 0.3\}$, we generated 1000
series of length 100. For each series, we applied the KS statistic
in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(0, 1)$
marginally. The histograms of the p-values from $1000$ replicates for all the
$\psi$ values are displayed in Figure~\ref{fig:pp_s}. When
$\phi \ne 0$, the histograms do not look likely to be generated from a standard
uniform distribution. Positive $\psi$ values led to p-values with a distribution
function higher than the standard uniform distribution function and, hence,
conservative tests. Negative $\psi$ values led to p-values with a distribution
function lower than the standard uniform distribution and, hence, liberal
tests. The larger the magnitude of
$\psi$, the bigger the deviation from the desired level.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{pp_s.pdf}
  \caption{PP-plots for the p-values obtained from KS test with serial
    dependence discarded and sample size $n = 200$ based on 1000
    replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$, with an AR(1) dependence structure on the standard normal
    scale. The AR coefficients were $\psi \in \{-0.3, -0.1,  0.1,  0.3\}$.
  }
  \label{fig:pp_s}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.75\textwidth]{pp_ss.pdf}
  \caption{PP-plots for the p-values obtained from KS test with serial
    dependence accounted for through a working ARMA model and $n = 200$ based on
    1000 replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
  }
  \label{fig:pp_ss}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.75\textwidth]{pp_s_f.pdf}
  \includegraphics[width=.75\textwidth]{pp_ssf.pdf}
  \caption{PP-plots for the p-values obtained from KS test without and with
    serial dependence accounted for and unspecified parameters and sample size
    $n = 200$ based on
    1000 replicates. The data have marginal distributions $N(8, 8)$ and
    $\Gamma(8, 1)$. The dependence structure on the standard normal scale was
    characterized by ARMA(1, 1) model, AR(2) model, and MA(1) model.
  }
  \label{fig:pp_ssf}
\end{figure}

Similar to Section~\ref{sec:dependence}, the copula approach is not a complete
solution. Regardless of the true dependence in the data we assume an AR(1)
dependence structure by taking the lag-1 sample auto-spearman rho. However, we
can show that as long as the AR(1) assumption is a close approximation, the
correction still provides a reasonable approximation that can be useful for
practical purposes. Figure~\ref{fig:ssd} shows the results of the
procedure performed on data generated with dependence structures of  MA(1),
ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for
dependence clearly deviates from a uniform distribution of p-values. Parametric
bootstrap provides some correction but does not account for dependence, so
therefore the results of the copula remedy are more accurate and favorable.
In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough
to our assumption of AR(1) that the results are reasonable. AR(2) however
appears to be just far enough from our assumption, showing a limitation of the
procedure.
